\ripple: Differentiable and Hardware-Accelerated Waveforms for Gravitational Wave Data Analysis

### 2023-02-07 src/tex/ms.tex
Changes to Eq 9

The Fisher information matrix for a single detector is typically given by 
% \amc{I'm guessing in practice you compute a Hessian, so maybe write that out?}
\begin{equation}
    \label{eq:fisher}
    \mathcal{I}^{k}_{ij} = (\partial_i h^k | \partial_j h^k) \, ,
\end{equation}
where $k$ indicates the detector, $\partial_i = \partial/\partial \theta_i$, and $h$ is the strain measured by the detector which is given by,
\begin{equation}
    h^k(\theta) = F_+(\phi) h^k_{+}(\Xi) + F_\times(\phi) h^k_{\times}(\Xi) \, .
\end{equation}
Note that here we have separated out the extrinsic ($\phi$) and intrinsic ($\Xi$) variables as well as introducing the detector projection functions for the plus and cross polarizations as $F^k_+$ and $F^k_\times$ respectively.
Since we are considering a three detector setup we simply add the Fisher matrices from the individual detectors to get the combined Fisher matrix:
\begin{equation}
    \mathcal{I}_{ij} =  \mathcal{I}^{\mathrm{Hanford}}_{ij} + \mathcal{I}^{\mathrm{Livingston}}_{ij} + \mathcal{I}^{\mathrm{Virgo}}_{ij}   \, .
\end{equation}
Finally, we invert the Fisher matrix to calculate the covariance matrix,
which provides forecasted measurement errors and parameter covariances for a signal with parameters $\theta$ observed by the given detector network in the high signal-to-noise limit.
% \mi{I think Aaron means ``provides'' not ``proves''; also, we might add ``in the high SNR limit''}

>>>>

The Fisher information matrix for a single detector is typically given by 
% \amc{I'm guessing in practice you compute a Hessian, so maybe write that out?}
\begin{equation}
    \label{eq:fisher}
    \mathcal{I}^{k}_{ij} = (\partial_i h^k | \partial_j h^k) \, ,
\end{equation}
where $k$ indicates the detector, $\partial_i = \partial/\partial \theta_i$, and $h^k$ is the strain measured by the detector which is given by,
\begin{equation}
    h^k(\theta) = F^k_+(\phi) h_{+}(\Xi) + F^k_\times(\phi) h_{\times}(\Xi) \, .
\end{equation}
Note that here we have separated out the extrinsic ($\phi$) and intrinsic ($\Xi$) variables as well as introducing the detector projection functions for the plus and cross polarizations as $F^k_+$ and $F^k_\times$ respectively.
Since we are considering a three detector setup we simply add the Fisher matrices from the individual detectors to get the combined Fisher matrix:
\begin{equation}
    \mathcal{I}_{ij} =  \mathcal{I}^{\mathrm{Hanford}}_{ij} + \mathcal{I}^{\mathrm{Livingston}}_{ij} + \mathcal{I}^{\mathrm{Virgo}}_{ij}   \, .
\end{equation}
Finally, we invert the Fisher matrix to calculate the covariance matrix,
which provides forecasted measurement errors and parameter covariances for a signal with parameters $\theta$ observed by the given detector network in the high signal-to-noise limit.
% \mi{I think Aaron means ``provides'' not ``proves''; also, we might add ``in the high SNR limit''}
